---
title: "Frailty Tools"
author: "Andrea"
date: "22/10/2021"
output:
  word_document: default
  html_document: default
---
## Intro 
This document explores how physical activity estimates differ based on which frailty tool is used 

```{r setup, include=FALSE}

pacman::p_load(dplyr, tidyr, readr, ggplot2, DT, qwraps2, kableExtra, broom, pander)
knitr::opts_chunk$set(echo = T, message = F, warning = F)
```

# Total Sample
```{r, echo = FALSE}
Data <- read_csv("C:/Users/andre/OneDrive/Documents/Documents/PhD Degree/Projects/Comparing Frailty Tools/Frailty_Tools/FrailtyTools.csv")
write.csv(Data,"C:/Users/andre/OneDrive/Documents/Documents/PhD Degree/Projects/Comparing Frailty Tools/Frailty_Tools/FrailtyTools.csv", row.names = FALSE)
datatable(Data)

Females <- subset(Data, Data$GENDER == "Female")
Males <- subset (Data, Data$GENDER == "Males")
```

# Describe Differences between NHANES Frailty Tools and Original Tool
## Frailty Phenotype
```{r, echo = FALSE}
text_Phenotype <- data.frame (
  Phenotype =  c ("Exhaustion", "Low Activity", "Weakness", "Low Body Weight"), 
  Original = c ("Self-reported exhaustion", 
                "The slowest 20% of the population was defined as baseline, based on time to walk 15 feet, adjusting for gender and standing height", 
                "Lowest 20% (by gender, body mass index)", 
                "> 10 lbs lost unintentionally in prior year"), 
  NHANES = c ("Some difficulty, much difficulty, or unable to do when responding to: difficulty walking from one room to the other on the same level.", 
              "Responded less active when asked: compared with most men/women your age, would you say that you are more active, less active, or about the same?", 
              "Some difficulty, much difficulty, or unable to do when responding to: difficulty lifting or carrying something as heavy as 10 pounds [like a sack of potatoes or rice]?", 
              "≤ 18.5 kg/m2 ")
)

kbl(text_Phenotype) %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "30em") %>% 
  column_spec(3, width = "30cm")
```

## SOF Index 

```{r, echo = FALSE}
text_SOF <- data.frame(
  SOFIndex = c ("Reduced Energy Level", "Inability to complete 5 chair rises", "Weight Loss"), 
  Original = c ("Asked: Do you feel full of energy?", 
                "Inability to complete 5 chair rises", 
                "greater or equal to 5% weight loss over 2 years"), 
  NHANES = c ("Some difficulty, much difficulty, or unable to do when responding to: difficulty walking from one room to the other on the same level.", 
              "Some difficulty, much difficulty, or unable to do when responding to: by yourself, and without any special equipment, how much difficulty do you have standing from an armless straight chair?", 
              "If participant had a 5% decrease between their self-reported weight one year ago and current self-reported weight, they were considered to have unintentional weight loss")
)

kbl(text_SOF) %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "30em") %>% 
  column_spec(3, width = "30cm")

```

## FRAIL Scale 

```{r, echo = FALSE}
text_FRAIL <- data.frame(
  FRAILScale = c ("Fatigue", "Resistance", "Ambulation", "Illness", "Loss of Weight"), 
  Original = c ("Asked: How much time during the previous 4 weeks did you feel tired? (All of the time, most of the time = 1 point)", 
                "Asked: In the last 4 weeks by yourself and not using aids, do you have any difficulty walking up 10 steps without resting?", 
                "Asked: In the last 4 weeks by yourself and not using aids do you have any difficulty walking 300 meters or one block?",
                "Asked, Did your Doctor ever tell you that you have?
                - Hypertension
                - Diabetes 
                - Cancer
                - Chronic Lung Disease
                - Heart Attack
                - Angina 
                - Asthma 
                - Arthritis 
                - Kidney Disease", 
                "Asked: Have you lost more than 5 kg or 5% of your body weight in the past year?"), 
  NHANES = c ("Some difficulty, much difficulty, or unable to do when responding to: difficulty walking from one room to the other on the same level.", 
              "Some difficulty, much difficulty, or unable to do when responding to: how much difficulty do you have walking up ten steps without resting?", 
              "Some difficulty, much difficulty, or unable to do when responding to: how much difficulty do you have walking for walking a quarter mile [that is about 2 or 3 blocks]?",
              "Have 5 or more of the following illnesses: 
              - Asthma, 
              - Arthritis 
              - Congestive heart failure 
              - Coronary heart disease 
              - Heart Attack 
              - Stroke 
              - Bronchitis 
              - Liver Condition 
              - Cancer 
              - Thyroid Problems", 
              "If participant had a 5% decrease between their self-reported weight one year ago and current self-reported weight, they were considered to have unintentional weight loss")

)


kbl(text_FRAIL) %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "30em") %>% 
  column_spec(3, width = "30cm")

```


## Frailty Index 

```{r, echo = FALSE}
text_FI<- data.frame(
  FrailtyIndex = c ("Comorbidities", "Function", 
                    "Signs/Symptoms", "Lab Values", 
                    "Other"),
  Variables = c ("Stroke,
                 Thyroid Condition, 
                 Cancer,
                 Heart Attack, 
                 Heart Disease,
                 Ever had blood pressure,
                 Angina/Angina Pectoris, 
                 Osteoporosis,
                 Diabetes,
                 Arthritis,
                 Ever broken hip,
                 Weak/Failing Kidneys", 
                 "Difficulty using fork and knife,
                 Difficulty dressing yourself, 
                 Difficulty getting in/out of bed,
                 Difficulty standing up from armless chair,
                 Difficulty managing money, 
                 Difficulty preparing meals,
                 Difficulty standing for long periods of time, 
                 Difficulty stooping, crouching, kneeling,
                 Difficulty grasping/holding small objects, 
                 Difficulty push or pulling large objects,
                 Difficulty attending social events", 
                 "Heart rate at rest,
                 Systolic blood pressure,
                 Cough regularly, 
                 Leaked/lost control or urine,
                 General vision, 
                 Difficulty seeing steps/curb in dim lights,
                 General hearing, 
                 Confusing or inability to remember things", 
                 "Homocysteine (μmol/L),
                 Folatc, scrum (nmol/L),
                 Glycohemoglobin (%),
                 Red blood cell count  (million cell/μL),
                 Hemoglobin (g/dL), 
                 Red cell distribution width (%), 
                 Lymphocyte percent (%), 
                 Segmented neutrophils percent (%)",
                 "Medications,
                 Self-reported health,
                 Health compared to 1 year ago,
                 Frequency of healthcare used,
                 Overnight hospital stays"
                 )
  )

kbl(text_FI) %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "30em")
```




# General Characteristics 


Phenotype Level 4 was combined with Level 3 as there was only 0.04% of people with Phenoype = 4
SOF Index 2 & 3 were combined as Level 3 had 0.63 % of people 
FRAIL SCALE 3, 4, 5 were combined: 3 (3.9%), 4 (0.6%), 5 (0.07%)
```{r, echo= FALSE, results='asis'}
options(qwraps2_markup = 'markdown') # default is latex


GC_Data <-
  list("Age" =
         list("min:"       = ~ min(AGE),
              "max:"       = ~ max(AGE),
              "mean (sd):" = ~ qwraps2::mean_sd(AGE, denote_sd = "paren")),
       "Sex" = 
         list ("Female" = ~ qwraps2:: n_perc(GENDER == "Female"), 
               "Male" = ~ qwraps2::n_perc (GENDER == "Male")), 
       "Race"= 
         list ("Non-Hispanic White" = ~ qwraps2::n_perc(RACE == "Non-Hispanic White"), 
               "Non-Hispanic Black" = ~ qwraps2::n_perc(RACE == "Non-Hispanic Black"), 
               "Mexican American" =  ~ qwraps2::n_perc(RACE == "Mexican American"), 
               "Other Hispanic" = ~ qwraps2:: n_perc(RACE == "Other Hispanic"),
               "Other Race" = ~ qwraps2::n_perc(RACE == "Other Race")),
       "Education"=
         list ("Less than 9th Grade"= ~ qwraps2::n_perc (EDUCATION == "Less than 9th"),
               "9th-11th Grade"= ~ qwraps2::n_perc (EDUCATION == "9-11th grade"), 
               "Highschool" = ~ qwraps2::n_perc (EDUCATION == "Highschool Grad"), 
               "Some College"= ~ qwraps2::n_perc (EDUCATION == "Some College"), 
               "College or Above"= ~ qwraps2::n_perc (EDUCATION == "College grad or above"), 
               "Missing" = ~ qwraps2::n_perc(EDUCATION == "Missing")), 
       "Marital Status" = 
         list ("Married" = ~ qwraps2::n_perc (MARITAL_STATUS == "Married"), 
               "Living with Partner" = ~ qwraps2::n_perc(MARITAL_STATUS== "Living with Partner"), 
               "Divorced" = ~ qwraps2::n_perc (MARITAL_STATUS == "Divorced"), 
               "Separated" = ~ qwraps2::n_perc (MARITAL_STATUS == "Separated"), 
               "Never Married" = ~ qwraps2::n_perc (MARITAL_STATUS == "Never Married"), 
               "Widowed" = ~ qwraps2::n_perc (MARITAL_STATUS == "Widowed"), 
               "Missing" = ~ qwraps2::n_perc (MARITAL_STATUS == "Missing")),
       "Frailty Phenotype" = 
         list ("0"= ~ qwraps2::n_perc (Phenotype == 0), 
               "1"= ~ qwraps2::n_perc (Phenotype == 1), 
               "2"= ~ qwraps2::n_perc (Phenotype == 2), 
               "3"= ~ qwraps2::n_perc (Phenotype == 3)), 
       "SOF Index" =
         list ("0" = ~ qwraps2::n_perc (SOF == 0), 
               "1" = ~ qwraps2::n_perc (SOF == 1),
               "2" = ~ qwraps2::n_perc (SOF == 2)), 
       "FRAIL Scale" = 
         list ("0" = ~ qwraps2::n_perc (FRAIL_Scale == 0), 
               "1" = ~ qwraps2::n_perc (FRAIL_Scale == 1), 
               "2"= ~ qwraps2::n_perc (FRAIL_Scale == 2), 
               "3"= ~ qwraps2::n_perc (FRAIL_Scale == 3)), 
       "Frailty Index"= 
         list ("min:"       = ~ min(FI),
              "max:"       = ~ max(FI),
              "mean (sd):" = ~ qwraps2::mean_sd(FI, denote_sd = "paren")), 
       "Time Spent in Moderate to Vigorous Physical Activity"= 
         list ("min:"       = ~ min(TotalMVPA),
              "max:"       = ~ max(TotalMVPA),
              "mean (sd):" = ~ qwraps2::mean_sd(TotalMVPA, denote_sd = "paren"))
       )
Table <- summary_table(Data, GC_Data) 
Table

dftodocx <- function(Table) {
  require(dplyr)
  require(pander)
  Table %>% 
  pander::pandoc.table.return() %>%
  pander::Pandoc.convert(text = ., format= "docx", footer = F)
}

dftodocx(Table)
```

# Average Amount of Time spent in MVPA by Frailty Tool 

## Frailty Phenotype 

```{r, echo = FALSE, results='asis'}
Frailty_tools <-
  list ("Time Spent in MVPA"= 
         list ("mean (sd):" = ~ qwraps2::mean_sd(TotalMVPA, denote_sd = "paren")))
PT <- summary_table(dplyr::group_by (Data, Phenotype),Frailty_tools)
PT
```

## SOF Index 
```{r, echo = FALSE, results='asis'}
SOF <- summary_table(dplyr::group_by(Data, SOF), Frailty_tools) 
SOF

```

## Frail Scale 
```{r, echo = FALSE, results='asis'}
FRAIL <-summary_table(dplyr::group_by(Data, FRAIL_Scale), Frailty_tools) 
FRAIL

```

## Frailty Index 
```{r, echo = FALSE, results='asis'}
Data <- 
  Data %>% 
  mutate (fi_group = cut(FI, breaks = c(0, 0.2, 0.3, 0.4, 1)))

FI <- summary_table(dplyr::group_by(Data, fi_group), Frailty_tools)
FI
```

### Interactions 
```{r, echo = FALSE}
Interaction_3way <- 
  (lm (cbind (Phenotype, FRAIL_Scale, SOF, FI)~log_MVPA*AGE*GENDER + RACE + EDUCATION + MARITAL_STATUS+ CYCLE + Wear, data = Data )) %>% summary 
Interaction_3way

Interaction_2way_PA_S <- 
  (lm (cbind (Phenotype, FRAIL_Scale, SOF, FI)~log_MVPA*GENDER + RACE + EDUCATION + MARITAL_STATUS+ CYCLE + Wear, data = Data )) %>% summary 
Interaction_2way_PA_S

Interaction_2way_PA_A <- 
  (lm (cbind (Phenotype, FRAIL_Scale, SOF, FI)~log_MVPA*AGE + RACE + EDUCATION + MARITAL_STATUS+ CYCLE + Wear, data = Data )) %>% summary 
Interaction_2way_PA_A

Interaction_2way_S_A <- 
  (lm (cbind (Phenotype, FRAIL_Scale, SOF, FI)~GENDER*AGE + RACE + EDUCATION + MARITAL_STATUS+ CYCLE + Wear, data = Data )) %>% summary 
Interaction_2way_S_A
```



Three way interaction found in SOF Index - therefore, subgroup by sex 
Two way interaction found with Phenotupe @ Sex and Age, subgroup by sex 

```{r, include= FALSE}
Interaction_2way_F <- 
  (lm (cbind (SOF, Phenotype)~MVPA_hr*AGE + RACE + EDUCATION + MARITAL_STATUS+ CYCLE + Wear, data = Females ))
Interaction_2way_F %>% 
  summary 

Interaction_2way_M <- 
  (lm (cbind (SOF, Phenotype)~MVPA_hr*AGE + RACE + EDUCATION + MARITAL_STATUS+ CYCLE + Wear, data = Males ))
Interaction_2way_M %>% 
  summary 
```


Simple Slope SOF Females by AGE only 

### Regressions without transformations, unadjusted 
```{r, echo = FALSE}
model_ALL_UN <-  
lm(cbind(FRAIL_Scale, FI) ~ 
     MVPA_hr + AGE + GENDER, 
   na.action = "na.exclude",
   data = Data) %>% 
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

model_ALL_UN%>% 
  DT::datatable()

```

#Phenotype - by Sex 
```{r, include = FALSE}
model_Phen_UN_F <-  
lm(cbind(Phenotype) ~ 
     log_MVPA + AGE, 
   na.action = "na.exclude",
   data = Females) %>% 
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

model_Phen_UN_F%>% 
  DT::datatable()
```

```{r, include = FALSE}
model_Phen_UN_M<-  
lm(cbind(Phenotype) ~ 
     MVPA_hr + AGE, 
   na.action = "na.exclude",
   data = Males) %>% 
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

model_Phen_UN_M%>% 
  DT::datatable()
```


# Regression - SOF Males 
```{r, include = FALSE}
model2 <-  
lm(SOF ~ MVPA_hr + AGE, 
   na.action = "na.exclude",
   data = Males) %>% 
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

model2 %>% 
  DT::datatable()

```


#SOF Females 
```{r, include = FALSE}
modelSOF_F_30 <-
  lm (SOF~ MVPA_hr + Age30 + (Age30*MVPA_hr), 
      na.action = "na.exclude",
      data = Females) %>%
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

modelSOF_F_30  %>% 
  DT::datatable()

modelSOF_F_40 <-
  lm (SOF~ MVPA_hr + Age40 + (Age40*MVPA_hr), 
      na.action = "na.exclude",
      data = Females) %>%
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

modelSOF_F_40  %>% 
  DT::datatable()

modelSOF_F_50 <-
  lm (SOF~ MVPA_hr + Age50 + (Age50*MVPA_hr), 
      na.action = "na.exclude",
      data = Females) %>%
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

modelSOF_F_50  %>% 
  DT::datatable()


modelSOF_F_60 <-
  lm (SOF~ MVPA_hr + Age50 + (Age50*MVPA_hr), 
      na.action = "na.exclude",
      data = Females) %>%
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

modelSOF_F_60  %>% 
  DT::datatable()
```

## Fully Adjusted 
```{r, include = FALSE}
model_ALL_AD<-  
lm(cbind(FRAIL_Scale, FI) ~ 
     MVPA_hr + AGE + GENDER + RACE + EDUCATION + MARITAL_STATUS + CYCLE + Wear, 
   na.action = "na.exclude",
   data = Data) %>% 
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

model_ALL_AD%>% 
  DT::datatable()
```

## Phenotype, by Sex 
```{r, include = FALSE}
model_Pheno_AD_F <-  
lm(cbind(Phenotype) ~ 
     MVPA_hr + AGE + RACE + EDUCATION + MARITAL_STATUS + CYCLE + Wear, 
   na.action = "na.exclude",
   data = Females) %>% 
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

model_Pheno_AD_F%>% 
  DT::datatable()

model_Pheno_AD_M <-  
lm(cbind(Phenotype) ~ 
     MVPA_hr + AGE + RACE + EDUCATION + MARITAL_STATUS + CYCLE + Wear, 
   na.action = "na.exclude",
   data = Males) %>% 
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

model_Pheno_AD_M%>% 
  DT::datatable()
```



## SOF Males 
```{r, include=FALSE}
SOF_M_AD <-  
lm(SOF ~ MVPA_hr + AGE + RACE + EDUCATION + MARITAL_STATUS + CYCLE + Wear, 
   na.action = "na.exclude",
   data = Males) %>% 
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

SOF_M_AD %>% 
  DT::datatable()
```


## SOF Females - by Age 
```{r, include = FALSE}
modelSOF_F_30_AD <-
  lm (SOF~ MVPA_hr + Age30 + (Age30*MVPA_hr) + RACE + EDUCATION + MARITAL_STATUS + CYCLE + Wear, 
      na.action = "na.exclude",
      data = Females) %>%
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

modelSOF_F_30_AD  %>% 
  DT::datatable()

modelSOF_F_40_AD <-
  lm (SOF~ MVPA_hr + Age40 + (Age40*MVPA_hr) + RACE + EDUCATION + MARITAL_STATUS + CYCLE + Wear, 
      na.action = "na.exclude",
      data = Females) %>%
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

modelSOF_F_40_AD  %>% 
  DT::datatable()

modelSOF_F_50_AD <-
  lm (SOF~ MVPA_hr + Age50 + (Age50*MVPA_hr)+ RACE + EDUCATION + MARITAL_STATUS + CYCLE + Wear, 
      na.action = "na.exclude",
      data = Females) %>%
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

modelSOF_F_50_AD  %>% 
  DT::datatable()


modelSOF_F_60_AD <-
  lm (SOF~ MVPA_hr + Age50 + (Age50*MVPA_hr)+ RACE + EDUCATION + MARITAL_STATUS + CYCLE + Wear, 
      na.action = "na.exclude",
      data = Females) %>%
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

modelSOF_F_60_AD  %>% 
  DT::datatable()

modelSOF_F_70_AD <-
  lm (SOF~ MVPA_hr + Age70 + (Age70*MVPA_hr), 
      na.action = "na.exclude",
      data = Females) %>%
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

modelSOF_F_70_AD  %>% 
  DT::datatable()
```


#Physical Activity Transformations 
```{r, include = FALSE}
skewness(Data$MVPA_hr)

#SQR 
Data$sq_MVPA <- sqrt(Data$MVPA_hr)

skewness (Data$sq_MVPA)

#log 10
Males$log_MVPA <- log10(Males$MVPA_hr)

skewness(Data$log_MVPA)

View (df)

# USE LOG 
Males$MVPA_hr [Males$MVPA_hr == 0] <- 0.00001
View (Females)
```

# Regressions Using Log MVPA
# Simple slope by AGE (30)
```{r}
Tools_70_UN <-
  lm (cbind(Phenotype, SOF, FRAIL_Scale, FI)~ log_MVPA + Age70 + (Age70*log_MVPA) + GENDER,
      na.action = "na.exclude",
      data = Data) %>%
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

Tools_70_UN %>% 
  DT::datatable()

Tools_70_AD <-
  lm (cbind(Phenotype, SOF, FRAIL_Scale, FI)~ log_MVPA + Age70 + (Age70*log_MVPA) + GENDER + RACE + EDUCATION + MARITAL_STATUS + CYCLE + Wear,
      na.action = "na.exclude",
      data = Data) %>%
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

Tools_70_AD %>% 
  DT::datatable()

View (Females)
```

## Interactions for Meet MVPA guide (Y/N) 

```{r, include = FALSE}
Interaction_3way_YN <- 
  (lm (cbind (Phenotype, FRAIL_Scale, SOF, FI)~MeetGuide*AGE*GENDER + RACE + EDUCATION + MARITAL_STATUS+ CYCLE + Wear, data = Data )) %>% summary 

Interaction_3way

Interaction_2way_YN_PA_A <- 
  (lm (cbind (Phenotype, FRAIL_Scale, FI, SOF)~MeetGuide*AGE+ RACE + EDUCATION + MARITAL_STATUS+ CYCLE + Wear, data = Data )) %>% summary 

Interaction_2way_YN_PA_A

Interaction_2way_YN_PA_S <- 
  (lm (cbind (Phenotype, FRAIL_Scale, FI, SOF)~MeetGuide*GENDER+ RACE + EDUCATION + MARITAL_STATUS+ CYCLE + Wear, data = Data )) %>% summary 

Interaction_2way_YN_PA_S

Interaction_2way_YN_A_S <- 
  (lm (cbind (Phenotype, FRAIL_Scale, FI, SOF)~AGE*GENDER+ RACE + EDUCATION + MARITAL_STATUS+ CYCLE + Wear, data = Data )) %>% summary 

Interaction_2way_YN_A_S

View (Data)
```


# Regression for FRAIL Scale, SOF, and FI 

```{r}
Tools_Meet_Un <-
  lm (cbind(SOF, FRAIL_Scale, FI)~ MeetGuide+ AGE + GENDER,
      na.action = "na.exclude",
      data = Data) %>%
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

Tools_Meet_Un %>% 
  DT::datatable()

Tools_Meet_AD <-
  lm (cbind(SOF, FRAIL_Scale, FI)~ MeetGuide+ AGE + GENDER+  RACE + EDUCATION + MARITAL_STATUS+ CYCLE + Wear,
      na.action = "na.exclude",
      data = Data) %>%
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

Tools_Meet_AD %>% 
  DT::datatable()

```

Phenotype- by AGE 
```{r}
PT_AGE_Un <-
  lm (Phenotype~ MeetGuide+ Age70 + (MeetGuide*Age70) + GENDER,
      na.action = "na.exclude",
      data = Data) %>%
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

PT_AGE_Un%>% 
  DT::datatable()


PT_AGE_AD <-
  lm (Phenotype~ MeetGuide+ Age70 + (MeetGuide*Age70) + GENDER + RACE + EDUCATION + MARITAL_STATUS+ CYCLE + Wear,
      na.action = "na.exclude",
      data = Data) %>%
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

PT_AGE_AD%>% 
  DT::datatable()
```


# With those 50 plus 

```{r}
Data_50 <- subset (Data, Data$AGE >= 50)
View (Data_50)

Interaction_3way_50 <- 
  (lm (cbind (Phenotype, FRAIL_Scale, SOF, FI)~log_MVPA*AGE*GENDER + RACE + EDUCATION + MARITAL_STATUS+ CYCLE + Wear, data = Data_50)) %>% summary 

Interaction_3way_50

Interaction_2way_P_A_50 <- 
  (lm (cbind (Phenotype, FRAIL_Scale, FI, SOF)~log_MVPA*AGE+ RACE + EDUCATION + MARITAL_STATUS+ CYCLE + Wear, data = Data_50 )) %>% summary 

Interaction_2way_P_A_50

Interaction_2way_PA_S_50 <- 
  (lm (cbind (Phenotype, FRAIL_Scale, FI, SOF)~log_MVPA*GENDER+ RACE + EDUCATION + MARITAL_STATUS+ CYCLE + Wear, data = Data_50 )) %>% summary 

Interaction_2way_PA_S_50

Interaction_2way_A_S_50 <- 
  (lm (cbind (Phenotype, FRAIL_Scale, FI, SOF)~AGE*GENDER+ RACE + EDUCATION + MARITAL_STATUS+ CYCLE + Wear, data = Data_50 )) %>% summary 

Interaction_2way_A_S_50

View (Data)
```

# Y/N 50 + Interactions 
```{r}
Interaction_3way_YN_50 <- 
  (lm (cbind (Phenotype, FRAIL_Scale, SOF, FI)~MeetGuide*AGE*GENDER + RACE + EDUCATION + MARITAL_STATUS+ CYCLE + Wear, data = Data_50)) %>% summary 

Interaction_3way_YN_50

Interaction_2way_P_A_50_YN <- 
  (lm (cbind (Phenotype, FRAIL_Scale, FI, SOF)~MeetGuide*AGE+ RACE + EDUCATION + MARITAL_STATUS+ CYCLE + Wear, data = Data_50 )) %>% summary 

Interaction_2way_P_A_50_YN

Interaction_2way_PA_S_50_YN <- 
  (lm (cbind (Phenotype, FRAIL_Scale, FI, SOF)~MeetGuide*GENDER+ RACE + EDUCATION + MARITAL_STATUS+ CYCLE + Wear, data = Data_50 )) %>% summary 

Interaction_2way_PA_S_50_YN

Interaction_2way_A_S_50 <- 
  (lm (cbind (Phenotype, FRAIL_Scale, FI, SOF)~AGE*GENDER+ RACE + EDUCATION + MARITAL_STATUS+ CYCLE + Wear, data = Data_50 )) %>% summary 

Interaction_2way_A_S_50
```


#Regressions for 50 + 
```{r}
Tools_50_UN_YN <-
  lm (cbind(Phenotype, SOF, FRAIL_Scale, FI)~ MeetGuide + AGE + GENDER,
      na.action = "na.exclude",
      data = Data_50) %>%
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

Tools_50_UN_YN%>% 
  DT::datatable()


Tools_50_AD_YN <-
  lm (cbind (Phenotype, SOF, FRAIL_Scale, FI) ~ MeetGuide + AGE + GENDER + RACE + EDUCATION + MARITAL_STATUS+ CYCLE + Wear,
      na.action = "na.exclude",
      data = Data_50) %>%
  broom::tidy(conf.int = T) %>% 
  mutate_if(is.numeric, ~formatC(., digits = 4, format = "f"))

Tools_50_AD_YN%>% 
  DT::datatable()
```

# MERGE Frailty Tools 
```{r}
FI <- read.csv(file.choose(), header = TRUE)
SOF <- read.csv(file.choose (), header = TRUE)
Phenotype <- read.csv(file.choose (), header = TRUE)

# FI 
View (FI)
FI <- 
  FI %>% 
  rename (SEQN = ï..seqn)

FI$fifinal [FI$fifinal == "#NULL!"] <- NA

FI <- 
  FI %>% 
  select (SEQN, fifinal)

View (FI)

# SOF 
View(SOF)
SOF_FI <- merge (SOF, FI, by = "SEQN")
View (SOF_FI)

#Phenotype 
View (Phenotype)
Tools <- merge (SOF_FI, Phenotype, by = "SEQN")


Tools <- 
  Tools %>% 
  drop_na (fifinal, SOF)

Tools_2 <- 
  Tools %>% 
  select (SEQN, fifinal, SOF, PF)

Tools_PA <- merge (D_SR, Tools_2, by = "SEQN")
View (Tools_PA)
```

###### 
# Rebuild FRAIL Scale
```{r}
# Fatigue - Used the same measure that was used in other scales 
View (Phenotype)
FRAIL_Exhaust <- 
  Phenotype %>% 
  select (SEQN, Ex_Phenotype)

# Resistance and Ambulation 
# 2004 cycle
PF_04 <- read.csv(file.choose(), header = TRUE)
FRAIL_Resistance_04 <-
  PF_04 %>% 
  select (SEQN, PFQ061C, PFQ061B) %>% 
  rename (Steps = PFQ061C, 
          Quater_Block = PFQ061B) # Checked numbers - match NHANES 
View (FRAIL_Resistance_04)

FRAIL_Resistance_04 %>% 
  count (Steps)

#2006 Cycle 
PF_06 <- read.csv(file.choose (), header = TRUE)
FRAIL_Resistance_06 <-
  PF_06 %>% 
  select (SEQN, PFQ061C, PFQ061B) %>% 
  rename (Steps = PFQ061C, 
          Quater_Block = PFQ061B) # Checked with NHANES, same Ns 


FRAIL_Resistance_06 %>% 
  count (Steps)

# Merge both cycles 
FRAIL_R_A <- rbind (FRAIL_Resistance_04, FRAIL_Resistance_06)

FRAIL_R_A$Steps<- ifelse (FRAIL_R_A$Steps== 1, 0, 
                          ifelse (FRAIL_R_A$Steps == 2, 1, 
                                  ifelse (FRAIL_R_A$Steps == 3, 1, 
                                          ifelse (FRAIL_R_A == 4, 1, NA))))

FRAIL_R_A$Quater_Block <-ifelse (FRAIL_R_A$Quater_Block == 1, 0, 
                                 ifelse (FRAIL_R_A$Quater_Block == 2, 1, 
                                         ifelse (FRAIL_R_A$Quater_Block == 3, 1, 
                                                 ifelse (FRAIL_R_A$Quater_Block == 4, 1, NA))))
FRAIL_R_A %>% 
  count (Quater_Block)

# Weight loss of 5% 

View (SOF_NAcut)

FRAIL_weight <- 
  SOF %>% 
  select (SEQN, Index_Weight)

View (FRAIL_weight)

#Number of Chronic Dieases 
MC_04 <- read.csv(file.choose(), header = TRUE)
MC_06 <- read.csv (file.choose (), header = TRUE)

MC04 <- 
  MC_04 %>% 
  select (SEQN, MCQ035, MCQ160A, MCQ160B, MCQ160C, MCQ160E,
          MCQ160F, MCQ170K, MCQ170L, MCQ220, MCQ170M) %>% 
  rename (Asthma = MCQ035, 
          Arthritis = MCQ160A, 
          CHF = MCQ160B, 
          CHD = MCQ160C, 
          Heart_Attack = MCQ160E, 
          Stroke = MCQ160F, 
          Bronchitis = MCQ170K, 
          Liver_Condition = MCQ170L,
          Cancer = MCQ220, 
          Thyriod = MCQ170M)
MC06 <- 
  MC_06 %>% 
  select (SEQN, MCQ035, MCQ160A, MCQ160B, MCQ160C, MCQ160E,
          MCQ160F, MCQ170K, MCQ170L, MCQ220, MCQ170M) %>% 
  rename (Asthma = MCQ035,  
          Arthritis = MCQ160A, 
          CHF = MCQ160B, 
          CHD = MCQ160C, 
          Heart_Attack = MCQ160E, 
          Stroke = MCQ160F, 
          Bronchitis = MCQ170K, 
          Liver_Condition = MCQ170L,
          Cancer = MCQ220, 
          Thyriod = MCQ170M)


View (MC06)

# Merge Data 
MC <- rbind (MC04, MC06)
names (MC)
View (MC)
MC %>% 
  count (Asthma)

MC$Thyriod[is.na (MC$Thyriod)] <- 0
MC$Thyriod <- ifelse (MC$Thyriod== 1, 1, 0)

MC$MC<- (MC$Arthritis +
           MC$Asthma + 
           MC$CHD +
           MC$CHF + 
           MC$Heart_Attack + 
           MC$Stroke + 
           MC$Bronchitis + 
           MC$Liver_Condition + 
           MC$Cancer + 
           MC$Thyriod)


MC %>% 
  count (MC)
View (MC)

MC$FRAIL_MC <- ifelse (MC$MC >= 5, 1, 0)

# Make FRAIL Scale 

FS1 <- merge (FRAIL_weight, FRAIL_R_A, by = "SEQN")
View (FS1)
FS2 <- merge (FS1, FRAIL_Exhaust, by = "SEQN")
FRAIL_SCALE <- merge (FS2, MC, by = "SEQN")
View (FRAIL_SCALE)

names (FRAIL_SCALE)

FRAIL <- 
  FRAIL_SCALE %>% 
  select (SEQN, Index_Weight, Steps, Quater_Block, Ex_Phenotype, FRAIL_MC) %>% 
  rename (FRAIL_weight = Index_Weight, 
          FRAIL_steps = Steps, 
          FRAIL_block = Quater_Block, 
          FRAIL_ex = Ex_Phenotype, 
          FRAIL_chronic = FRAIL_MC) %>% 
  drop_na (FRAIL_block, 
           FRAIL_ex, 
           FRAIL_weight, 
           FRAIL_chronic, 
           FRAIL_steps)
View (FRAIL)

FRAIL$FRAIL_Scale <- (FRAIL$FRAIL_block + FRAIL$FRAIL_weight + FRAIL$FRAIL_steps + FRAIL$FRAIL_ex + FRAIL$FRAIL_chronic)
FRAIL %>% 
  count (FRAIL_Scale)
FT <- merge (Frailty_Tools, FRAIL, by = "SEQN")

View (FT)
write.csv(SOF, "C:/Users/andre/OneDrive/Documents/Documents/PhD Degree/Projects/Comparing Frailty Tools//FRAILScale.csv", row.names = TRUE)
```

# Demo
```{r}
demo_04 <- read.csv(file.choose(), header= TRUE)
View (demo_04)

demo <- 
  demo_04 %>% 
  select (SEQN, SEX, AGE, RACE, EDUCATION, MARITAL, CYCLE, fifinal, MVPA)

Demo<- subset(demo, demo$CYCLE > 2)
View (Demo)

Demo_SOF <- merge (Demo, SOF, by = "SEQN", all = TRUE)
Demo_PT <- merge (Demo_SOF, Phenotype, by = "SEQN", all = TRUE)
DB <- merge (Demo_PT, FRAIL, by = "SEQN", all = TRUE)
```


#Make Data for all Tools 
```{r}
View (DB)

DB <- 
  DB %>% 
  drop_na (AGE)
```


```{r}

```

















